---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(dplyr)
if (basename(getwd()) == "docs") {
  knitr::opts_knit$set(root.dir = file.path(getwd(), ".."))
}
```

# fs
[![Travis build status](https://travis-ci.org/r-lib/fs.svg?branch=master)](https://travis-ci.org/r-lib/fs)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://img.shields.io/badge/lifecycle-experimental-orange.svg)
[![Coverage status](https://codecov.io/gh/r-lib/fs/branch/master/graph/badge.svg)](https://codecov.io/github/r-lib/fs?branch=master)

The goal of **fs** is to provide a uniform interface to file operations using [libuv](http://docs.libuv.org/en/v1.x/fs.html). libuv is used widely in the javascript community underneath [nodejs](https://nodejs.org), so the code is tested by a large community on diverse systems. The name, and some of the interface, is inspired by Rust's [fs module](https://doc.rust-lang.org/std/fs/index.html).

## Installation

You can install **fs** from github with:

``` r
# install.packages("devtools")
devtools::install_github("r-lib/fs")
```

## Motivation vs base equivalents

* All **fs** functions are vectorized, accepting multiple paths as input.
  All functions either return a character vector of paths, or
  a named integer or logical vector (where the names give the paths).

* If an operation fails, **fs** throws an error. Base R file manipulation functions
  tend to generate a warning and return a logical vector of successes and
  failures. This makes it easy to miss a failure.

* **fs** functions always convert the input paths to UTF-8 and return results as
  UTF-8 encoded paths. This gives you path encoding consistency across OSs.

* **fs** functions use a consistent naming convention. Because base R's functions
  were gradually added over time there are a number of different conventions 
  used (e.g. `path.expand()` vs `normalizePath()`; `Sys.chmod()` vs 
  `file.access()`).

## Usage

**fs** functions all accept vectors of paths as inputs and outputs, so they work
well with dplyr verbs in pipelines.

```{r}
library(fs)
library(dplyr)
dir_info("src", recursive = FALSE) %>%
  filter(size > "10KB") %>%
  arrange(desc(size)) %>%
  select(path, permissions, size)
```

### Functions

**fs** functions are divided into four main categories: manipulating paths, files, directories, and links.

### Path functions

- `path()` - constructs a new path
- `path_expand()` - expand `~` in a path
- `path_home()` - home directory path
- `path_norm()` - normalizes a path
- `path_split()` - split a path into components
- `path_temp()` - temporary directory path

### File functions

- `file_chmod()` - Change file permissions
- `file_chown()` - Change file ownership
- `file_copy()` - Copy a file
- `file_create()` - Create a new empty file
- `file_delete()` - Delete files
- `file_exists()` / `file_access()` - Query for file existence and access permissions.
- `file_info()` - Query file metadata
- `file_move()` - Move a file

### Directory functions

- `dir_create()` -  Create a new directory
- `dir_delete()` - Delete an existing directory
- `dir_exists()` - Query for directory existence
- `dir_list()` - List objects in a directory
- `dir_info()` - Retrieve information on objects in a directory
- `dir_walk()` - Perform an action on objects in a directory

### Link functions

- `link_create()` - Create a new link
- `link_exists()` - Query for link existence
- `link_path()` - Retrieve the path a link points to
