---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
if (basename(getwd()) == "docs") {
  knitr::opts_knit$set(root.dir = file.path(getwd(), ".."))
}
fs:::pkgdown_tmp(c("/tmp/filedd463d6d7e0f", "/tmp/filedd464dbb3467"))
```

# fs
![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)
[![Travis build status](https://travis-ci.org/r-lib/fs.svg?branch=master)](https://travis-ci.org/r-lib/fs)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/r-lib/fs?branch=master&svg=true)](https://ci.appveyor.com/project/r-lib/fs)
[![Coverage status](https://codecov.io/gh/r-lib/fs/branch/master/graph/badge.svg)](https://codecov.io/github/r-lib/fs?branch=master)

The goal of **fs** is to provide a uniform interface to file and directory
operations, built on top of the [libuv](http://docs.libuv.org/en/v1.x/fs.html)
C library. libuv is used by [nodejs](https://nodejs.org), so is widely in the
javascript community and tested by a large community on diverse systems. The
name, and some of the interface, is inspired by Rust's [fs module](https://doc.rust-lang.org/std/fs/index.html).

## Installation

You can install **fs** from github with:

``` r
# install.packages("devtools")
devtools::install_github("r-lib/fs")
```

## Motivation vs base equivalents

* All **fs** functions are vectorized, accepting multiple paths as input.
  All functions either return a character vector of paths, or
  a named integer or logical vector (where the names give the paths).

* If an operation fails, **fs** throws an error. Base R file manipulation functions
  tend to generate a warning and return a logical vector of successes and
  failures. This makes it easy to miss a failure.

* **fs** functions always convert the input paths to UTF-8 and return results as
  UTF-8 encoded paths. This gives you path encoding consistency across OSs.

* **fs** functions use a consistent naming convention. Because base R's functions
  were gradually added over time there are a number of different conventions 
  used (e.g. `path.expand()` vs `normalizePath()`; `Sys.chmod()` vs 
  `file.access()`).

## Usage

**fs** functions are divided into four main categories: manipulating paths 
(`path_`), files (`file_`), directories (`dir_`), and links (`link_`). 
Directories and links are special types of files, so `file_` functions 
will generally also work when applied to a directory or link.

```{r}
library(fs)

# list files in the current directory
dir_list()

# create a new directory
tmp <- dir_create(file_temp())
tmp

# create new files in that directory
file_create(path(tmp, "my-file.txt"))
dir_list(tmp)

# remove files from the directory
file_delete(path(tmp, "my-file.txt"))
dir_list(tmp)

# remove the directory
dir_delete(tmp)
```

**fs** is designed to work well with the pipe, although it doesn't provide the 
pipe itself because it's a low-level infrastructure package. You'll need to
attach magrittr or similar.

```{r}
library(magrittr)

paths <- file_temp() %>%
  dir_create() %>%
  path(letters[1:5]) %>%
  file_create()
paths

paths %>% file_delete()
```

`dir_info()` returns a data frame, which works particularly nicely in
conjunction with dplyr and other tidyverse packages.

```{r}
suppressMessages(
  library(tidyverse))

# Filter files by type, permission and size
dir_info("src", recursive = FALSE) %>%
  filter(type == "file", permissions == "u+r", size > "10KB") %>%
  arrange(desc(size)) %>%
  select(path, permissions, size, creation_time)

# Tally size of folders
dir_info("src", recursive = TRUE) %>%
  group_by(directory = path_dir(path)) %>%
  tally(wt = size, sort = TRUE)

# Read a collection of similar files into one data frame
system.file("extdata", package = "readr") %>%
  dir_list(glob = "*mtcars*") %>%
  set_names(path_file(.)) %>%
  map_df(read_csv, .id = "file", col_types = cols())
```
